Compensated de Casteljau algorithm in \(K\) times the working precision

### 2018-08-29 doc/paper.tex
Adding "Acknowledgements" section to paper.
This includes a reference to the GitHub repository so that people
may access the source code. In addition:

- Updated `README.md` to give specific pointers to where the
  algorithm is implemented in C, C++ and Python
- Updated the Knuth reference to the 1st edition to make it clear
  that the algorithm was stated in 1969, not 1997
- Added Babuska reference into the "Acknowledgements" section since
  a similar compensated algorithm was described there
- Added a missing tilde over `\ell` in the definition of `L_{F, k}`

An error-free transformation is a computational method where both
the computed result and the round-off error are returned. It
is considered ``free'' of error if the round-off can be represented
exactly as an element or elements of \(\mathbf{F}\).
The error-free transformations used in this paper are
the \texttt{TwoSum} algorithm by Knuth (\cite{Knuth1997}) and
\texttt{TwoProd} algorithm by Dekker (\cite{Dekker1971}, Section 5),
respectively.

@@

As we'll see soon (Lemma~\ref{lemma:k-order}), putting a bound on
sums of the form \(\sum_{j = 0}^k \ell_{F, j}^{(k)} B_{j, k}(s)\) will
be useful to get an overall bound on the relative error for
\texttt{CompDeCasteljauK}, so we define
\(L_{F, k} \coloneqq \sum_{j = 0}^k \ell_{F, j}^{(k)} B_{j, k}(s)\).

@@

>>>>

An error-free transformation is a computational method where both
the computed result and the round-off error are returned. It
is considered ``free'' of error if the round-off can be represented
exactly as an element or elements of \(\mathbf{F}\).
The error-free transformations used in this paper are
the \texttt{TwoSum} algorithm by Knuth (\cite{Knuth1969}) and
\texttt{TwoProd} algorithm by Dekker (\cite{Dekker1971}, Section 5),
respectively.

@@

As we'll see soon (Lemma~\ref{lemma:k-order}), putting a bound on
sums of the form \(\sum_{j = 0}^k \widetilde{\ell}_{F, j}^{(k)} B_{j, k}(s)\) will
be useful to get an overall bound on the relative error for
\texttt{CompDeCasteljauK}, so we define
\(L_{F, k} \coloneqq \sum_{j = 0}^k \widetilde{\ell}_{F, j}^{(k)} B_{j, k}(s)\).

@@

\section{Acknowledgements}

The author would like to thank \cite{Ogita2005}, \cite{Graillat2009} and
\cite{Jiang2010} for their papers that motivated this work. In particular,
the work of \cite{Ogita2005} reignited the path to compensated algorithms set
forth in \cite{Babuska1968}, \cite{Knuth1969} and \cite{Dekker1971}.

The family of algorithms described in this paper have been implemented in
C, C++ and Python by the author (\cite{KCompensatedGitHub}).
